### 2022-06-13 paper.tex

To assess performance of each combination of methods, we used a nearest neighbor count score that quantifies how well the different neuronal subtypes are separated in 15 dimensional PC space (see Methods).
The results demonstrate that the 16 neuronal subtypes are more cleanly separated when using our proposed methods (Figure \ref{figure:score}A).
Most of this gain in performance can be attributed to the use of VMRs over genomic tiles. The use of mean shrunken residuals over methylation fractions provides an additional small improvement.

>>>>

To assess performance of each combination of methods, we used a nearest neighbor count score (see Methods) that quantifies how well the different neuronal subtypes are separated in 15 dimensional PC space. We used the original assignment of cells to cell types from \citet{luo2017single}.
The results demonstrate that the 16 neuronal subtypes are more cleanly separated when using our proposed methods (Figure \ref{figure:score}A).
Most of this gain in performance can be attributed to the use of VMRs over genomic tiles. The use of mean shrunken residuals over methylation fractions provides an additional small improvement.
